Variation of Euclidean Algorithm for finding gcd of two numbers

### 2017-12-14 latex/draft.tex
more refine

Let's modify the algorithm, with a small variation with a slightly modified representaion of \mod and \moddash; let's define a new operator as \moddashdash(say \mod -dash-dash).

@@

The modified algorithm can be presented below.
\newline \textbf{Algorithm 4:}
\begin{algorithmic}[1]
\STATE \progvar{a}, \progvar{b}: integer
\IF{$|n| \geq |m|$}
	\STATE $\progvar{a} \gets |n|; \progvar{b} \gets |m|;$
\ELSE
	\STATE $\progvar{a} \gets |m|; \progvar{b} \gets |n|;$
\ENDIF
\WHILE{$\progvar{b} > 0$ } 
	\STATE $(\progvar{a}, \progvar{b}) \leftarrow (\progvar{b}, \progvar{a}  $ $mod'' $ $\progvar{b});$
\ENDWHILE
\RETURN \progvar{a}
\end {algorithmic}

So it can be noted from the above that there is apparent no change from the previously given algorithm except line no. 8. The modified algorithm uses $mod'$ instead of \mod for the modulus operation. This $mod''$ can be expressed as below.

@@

\section{Conclusion}
From the table 4 contents it is clear that by using the \var{min(r,s)} is advantageous and bring down the number of recursion. And also it is proved that we have a substitute for \var{r} in the context of modulus arithmetic and which can be used within the intermediate steps of the algorithm to find gcd of two numbers. The order of optimization is still under investigation and could be significant when we integers with very very long digits may be in the order of thousands! Having discussed the advantage of $mod''$, it also should be noted that $mod''$ is implemented with the help of existing \mod operator and an additional subtraction. The running time of subtraction is linear however the running time of modular operation is quadratic in nature. So this additional subtraction can be well compensated by reduction in the number of intermediate steps in the recursion. There are also other highly optimised algorithm exists such as \var{Binary GCD}, \var{Lehmer's Algorithm} etc. for finding the gcd and this paper does not intent to provide a optimise algorithm for gcd.

>>>>

Let's modify the algorithm, with a small variation with a slightly modified representaion of \mod and \moddash; let's define a new operator as \moddashdash  (say \mod -dash-dash).

@@

The modified algorithm can be presented below.
\newline \textbf{Algorithm 4:}
\begin{algorithmic}[1]
\STATE \progvar{a}, \progvar{b}: integer
\IF{$|n| \geq |m|$}
	\STATE $\progvar{a} \gets |n|; \progvar{b} \gets |m|;$
\ELSE
	\STATE $\progvar{a} \gets |m|; \progvar{b} \gets |n|;$
\ENDIF
\WHILE{$\progvar{b} > 0$ } 
	\STATE $(\progvar{a}, \progvar{b}) \leftarrow (\progvar{b}, \progvar{a}  $ \moddashdash  $\progvar{b});$
\ENDWHILE
\RETURN \progvar{a}
\end {algorithmic}

So it can be noted from the above algorithm that, there is apparent no change from the previously given algorithm except line no. 8. The modified algorithm uses \moddashdash instead of \mod for the modulus operation.

@@

\section{Conclusion}
From the table 4 contents it is clear that by using the \var{min(r,s)} is advantageous and bring down the number of recursion. And also it is proved that we have a substitute for \var{r} in the context of modulus arithmetic and which can be used within the intermediate steps of the algorithm to find gcd of two numbers. The order of optimization is still under investigation and could be significant when we integers with very very long digits may be in the order of thousands! Having discussed the advantage of \moddashdash, it also should be noted that \moddashdash is implemented with the help of existing \mod operator and an additional subtraction. The running time of subtraction is linear however the running time of modular operation is quadratic in nature. So this additional subtraction can be well compensated by reduction in the number of intermediate steps in the recursion. There are also other highly optimised algorithm exists such as \var{Binary GCD}, \var{Lehmer's Algorithm} etc. for finding the gcd and this paper does not intent to provide a optimise algorithm for gcd.
